---
title: "Final Everybody"
author: "Michael Monreal"
date: "May 16, 2019"
output: html_document
---
## Introduction
A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 

## Methods 
The methods used for this was chi-square and fisher test. We're going to look at bar plots and compare them to see if they are different visually then look at the numerical results.
   
```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

```{r}
results <- read.csv(file = "avastivironal.csv", header = TRUE)
trialtbl=xtabs(~infected+treatment,data=results)
```

```{r}
barchartGC(trialtbl,type = "percent")
```

```{r}
colPerc(trialtbl)
```

```{r}
rowPerc(trialtbl)
```

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```

```{r}
fisher.test(trialtbl)
```

## Conclusion
40% of people got aids. The drugs do seem to be working. The Fisher test proves this statement, which says that it decreases the chances that you get aids if you use the drug. 