---
title: "Menfinal"
author: "Michael Monreal"
date: "May 21, 2019"
output: html_document
---

## Introduction
A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 

## Methods 
The methods used for this was chi-square and fisher test. We're going to look at bar plots and compare them to see if they are different visually then look at the numerical results.
   
```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avast <-filter(avast,sex =="M")
```

```{r}
results <- avast
trialtbl=xtabs(~infected+treatment,data=results)
```

```{r}
barchartGC(trialtbl,type = "percent")
```

```{r}
colPerc(trialtbl)
```

```{r}
rowPerc(trialtbl)
```

```{r}
chisqtestGC(trialtbl, graph = TRUE)
```

```{r}
fisher.test(trialtbl)
```

## Conclusion
30% of people got aids. The drugs are working. The Fisher test proves this statement, which says that it highly decreases the chances that you get aids if you use the drug. 